---
title: "GENOVA distance-dependent decay and differences"
author: "Mikhail Dozmorov"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: no
  html_document:
    theme: cerulean
    toc: yes
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
# Set up the environment
library(knitr)
opts_chunk$set(cache.path='cache/', fig.path='img/', cache=F, tidy=T, fig.keep='high', echo=F, dpi=100, warnings=F, message=F, comment=NA, warning=F, results='as.is', fig.width = 10, fig.height = 6) #out.width=700, 
library(pander)
panderOptions('table.split.table', Inf)
set.seed(1)
library(dplyr)
options(stringsAsFactors = FALSE)
```

# Libraries

```{r libraries}
library(GENOVA) # remotes::install_github("robinweide/GENOVA", ref = "dev")
library(rCGH)
library(TxDb.Hsapiens.UCSC.hg38.knownGene)
library(strawr) # remotes::install_github("aidenlab/straw/R")
library(grid)
library(gridExtra)
library(ggplot2)
library(ggsci)
library(scales)
# scales::show_col(pal_lancet("lanonc")(8))
mycols = pal_lancet("lanonc")(8)
```

# Settings

```{r settings}
# .hic files, merged samples
fileNamehic1 <- "/Users/mdozmorov/Documents/Data/GoogleDrive/HiC_files/03.Arima_samples_juicer/UCD52_PR/inter_30.hic"
fileNamehic2 <- "/Users/mdozmorov/Documents/Data/GoogleDrive/HiC_files/03.Arima_samples_juicer/UCD52_CR/inter_30.hic"
```
```{r centromeres}
# Centromeres from rCGH
hg38_chrom <- hg38
hg38_chrom$chrom[hg38_chrom$chrom == 23] <- "X"
hg38_chrom$chrom[hg38_chrom$chrom == 24] <- "Y"
centromeres <- hg38_chrom[, c("chrom", "centromerStart", "centromerEnd")]
```

# Load data

## Juicer

```{r juicer_samples, eval=TRUE}
### Juicer, 100kb
UCD52PR_100kb_juicer <- load_contacts(signal_path = fileNamehic1, sample_name = "PR",
                                     resolution = 1e5,
                                     balancing = TRUE, # KR by default
                                     colour = "black")
UCD52CR_100kb_juicer <- load_contacts(signal_path = fileNamehic2, sample_name = "CR",
                                     resolution = 1e5,
                                     balancing = TRUE, # KR by default
                                     colour = "red")
```

## Select files

```{r}
# Samples
UCD52PR_100kb <- UCD52PR_100kb_juicer
UCD52CR_100kb <- UCD52CR_100kb_juicer
```


## RCP
The Relative Contact Probability (RCP) computes the contact probability as a function of genomic distance, as described in [@Lieberman-Aiden2009]. This can be computed for a specific set of chromosomes or genome-wide. To ignore centromeric contacts (which have a aberrant RCP), centromeric information is needed. This is taken from the experiment-object or found empirically by comparing trans-interactions.

```{r doRCP, cache=F}
RCP_out <- RCP(explist = list("PR" = UCD52PR_100kb, "CR" = UCD52CR_100kb)) #, 
               #chromsToUse = '1')
```

The user can decide to plot the RCP per chromosome. If the data is sparse, a LOESS-smooting could be convenient. It takes the color and name from the experiment-objects. If we look at the resulting plot, we can see that the $\Delta CR$ has more interactions in the $[\pm\text{800kb}, \pm\text{2Mb}]$ range (figure \@ref(fig:RCPPLOT1)). The sizes of TADs are fall into this range, so a next step could be to dive into the TAD-specific analyses (discussed below). Moreover, the $\Delta CR$ has less interactions in the far-*cis* range ($[\pm\text{10Mb}, \pm\text{100Mb}]$): A- and B-compartments are often this size, so a next step could be to look more into compartmentalisation with `compartment_matrixplot` or `trans.compartment.plot`, for example.
```{r, echo=F}
options(scipen = 1)
```

```{r RCPPLOT1, cache=F, message=FALSE, fig.wide= T , fig.cap= "RCP. Every facet shows the RCP of one chromosome."}
visualise(RCP_out)
```

### Differentials
We can directly compare samples to one another (for example PR versus CR). To plot this, the `metric` argument has to be set to `lfc` and `contrast` to 1, indicating the PR sample (figure \@ref(fig:RCPPLOT2)). This plots the log-fold change of average probabilities.
```{r RCPPLOT2, message=FALSE,  cache=F, fig.small= T , fig.cap= "RCP in lfc-mode.", warning=FALSE}
# Plot RCP: combined
mtx <- visualise(RCP_out, contrast = 1, metric = 'lfc', raw = TRUE)
mtx_to_plot <- mtx$data

plot_decay <- function(mtx = mtx1, title = "Genome-wide decay difference") {
  ggplot(mtx, aes(x = distance, y = P) ) + 
    geom_hline(yintercept = 0) +
    # geom_point(shape=16, color = mycols[2]) + 
    geom_line(size = 1, color = mycols[1]) +
    # geom_smooth(se = FALSE) +
    scale_color_manual(name = "Condition:", values = c("genome-wide" = mycols[7])) +
    labs(title = title, x = "Distance (bp)", y = expression(log2(P[CR]/P[PR]))) +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
                  labels = trans_format("log10", math_format(10^.x))) +
    annotation_logticks(sides="b") +
    theme_bw() + theme(legend.position = "none")
}
plot_decay(mtx = mtx_to_plot, title = "Genome-wide decay difference")
ggsave(filename = "manuscript/figures/figure_decay/Figure_decay_difference.svg", width = 3, height = 3 )
```

### Per chromosome differentials

```{r}
chr_selected <- c(1:22) # , "X", "Y"
# List to store plots
list_RCP_plots <- list()
for (chr in chr_selected) {
  RCP_out_chr <- RCP(explist = list("PR" = UCD52PR_100kb, "CR" = UCD52CR_100kb), chromsToUse = chr)
  mtx <- visualise(RCP_out_chr, contrast = 1, metric = 'lfc', raw = TRUE)
  mtx_to_plot <- mtx$data
  p <- plot_decay(mtx = mtx_to_plot, title = paste("chr", chr))
  list_RCP_plots <- c(list_RCP_plots, list(p))
}
# Auto-selection of the number of columns to arrange chromosome-specific plots
n <- length(list_RCP_plots)
nCol <- floor(sqrt(n))
nCol <- 4
pdf("manuscript/figures/figure_decay/Figure_decay_difference_chr.pdf", width = 8, height = 11 )
do.call("grid.arrange", c(list_RCP_plots, ncol=nCol))
dev.off()
# ggsave(filename = "manuscript/figures/Figure_decay_difference_chr.svg", width = 8, height = 11 )
```

