---
title: "GSEA barplot figure"
author: "Maggie Marshall"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: no
  html_document:
    theme: cerulean
    toc: yes
---
```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
# Set up the environment
library(knitr)
opts_chunk$set(cache.path='cache/', fig.path='img/', cache=F, tidy=T, fig.keep='high', echo=F, dpi=100, warnings=F, message=F, comment=NA, warning=F, results='as.is', fig.width = 10, fig.height = 6) #out.width=700, 
library(pander)
panderOptions('table.split.table', Inf)
set.seed(1)
library(dplyr)
options(stringsAsFactors = FALSE)
```

This script will take in the results from running GSEA enrichments on RNAseq and dcHiC AB compartments data and turn it into a bar plot for each subplot in the GSEA figures for each dataset. Each bar will correspond to a pathway enriched, and will represent the -log10(p.adj). 

```{r libraries}
# Libraries
library(tidyverse)
library(readxl)
library(cowplot)
library(ggplot2)
library(stringr)
library("ggsci")
library(scales)
scales::show_col(pal_lancet("lanonc")(8))
mycols = pal_lancet("lanonc")(8)
library(forcats)
```

# Settings

```{r settings}
# Data
# Working directory
# Mikhail's paths
# data_dir       <- "/Users/mdozmorov/Documents/Data/GoogleDrive/HiC_files/results/manuscript"
# Maggie's paths
data_dir       <- "~/Google Drive/My Drive/HiC_files/results/manuscript"

# data type parameter, either RNAseq or dcHiC to set the data directory and file paths 
# data_type = "RNAseq"
data_type = "dcHiC"
# set file paths depending on data type
if (data_type == "RNAseq"){
  fileNameIn1 <- file.path(data_dir, "Tables_DEGs_Enrichment", "Tables_DEGs_Enrichment.xlsx")
  OutputDir <- file.path(data_dir, "Tables_DEGs_Enrichment")
  Output_Suffix <- "_Figure_DEGs_Enrichment.svg"
  # parameter for subplots 
  subplots = 3
  # set sheets for A panel 
  # (A) KEGG pathways, C5: ontology gene sets, (B) C2: curated gene sets, (C) H: hallmark gene sets MSigDb results.
  A_terms <- c("Ribosome", "Oxidative phosphorylation", "GOMF_STRUCTURAL_CONSTITUENT_OF_RIBOSOME", "GOBP_DEFENSE_RESPONSE")
  A_sheets <- c("GSEA.KEGG", "GSEA.C5")
  # set sheets for B panel 
  B_sheets <- c("GSEA.C2")
  B_terms <- c("SANA_RESPONSE_TO_IFNG_UP", "ONDER_CDH1_TARGETS_2_DN", "SANA_TNF_SIGNALING_UP",
               "JAEGER_METASTASIS_DN")
  # set sheets for C panel 
  C_sheets <- c("GSEA.H")
  C_terms <- c("HALLMARK_INTERFERON_GAMMA_RESPONSE", "HALLMARK_INTERFERON_ALPHA_RESPONSE",
               "HALLMARK_WNT_BETA_CATENIN_SIGNALING", "HALLMARK_OXIDATIVE_PHOSPHORYLATION", 
               "HALLMARK_DNA_REPAIR", "HALLMARK_NOTCH_SIGNALING", "HALLMARK_KRAS_SIGNALING_UP",
               "HALLMARK_MTORC1_SIGNALING")
  # combined list of list for sheet names for each subplot 
  sheets = c(A = list(A_sheets), B = list(B_sheets), C = list(C_sheets))
  # list of list for term names for each subplot 
  terms = c(A = list(A_terms), B = list(B_terms), C = list(C_terms))
} else if (data_type == "dcHiC"){
  fileNameIn1 <- file.path(data_dir, "Tables_dcHiC_AB_Enrichment", "Tables_dcHiC_AB_Enrichment.xlsx")
  OutputDir <- file.path(data_dir, "Tables_dcHiC_AB_Enrichment")
  Output_Suffix <- "_Figure_dcHiC_AB_Enrichment.svg"
  # parameter for subplots 
  subplots = 4
  # set sheets for A panel 
  # (A) KEGG pathways. (B) C2: curated gene sets, (C) C5: ontology gene sets, (D) H: hallmark gene sets MSigDb results
  A_sheets <- c("GSEA.KEGG.ALL")
  A_terms <- c("Tyrosine metabolism", "Metabolism of xenobiotics by cytochrome P450",
               "Basal cell carcinoma", "Ribosome biogenesis in eukaryotes")
  # set sheets for B panel 
  B_sheets <- c("GSEA.ALL.C2")
  B_terms <- c("NIKOLSKY_BREAST_CANCER_16P13_AMPLICON", "REACTOME_ETHANOL_OXIDATION",
               "LASTOWSKA_COAMPLIFIED_WITH_MYCN",
               "REACTOME_TRANSCRIPTIONAL_REGULATION_BY_SMALL_RNAS")
  # set sheets for C panel 
  C_sheets <- c("GSEA.ALL.C5")
  C_terms <- c("GOBP_HOMOPHILIC_CELL_ADHESION_VIA_PLASMA_MEMBRANE_ADHESION_MOLECULES",
               "GOBP_ETHANOL_OXIDATION")
  # set sheets for D panel 
  D_sheets <- c("GSEA.ALL.H")
  D_terms <- c("HALLMARK_INTERFERON_GAMMA_RESPONSE", "HALLMARK_P53_PATHWAY")
  # combined list of list for sheet names for each subplot 
  sheets = c(A = list(A_sheets), B = list(B_sheets), C = list(C_sheets), D = list(D_sheets))
  # list of list for term names for each subplot 
  terms = c(A = list(A_terms), B = list(B_terms), C = list(C_terms), D = list(D_terms))
}

max_enrichment_length <- 50 # Maximum length of enrichment descriptions
```

# Visualization

-log10 adjusted p-value interpretation

$$1 = 10^{-1} = 0.1$$
$$1.3 = 10^{-1.3} \approx 0.05$$
$$2 = 10^{-2} = 0.01$$
$$4 = 10^{-4} = 0.0001$$
etc. -log10 adjusted p-value $\ge1$ is acceptable

```{r visualizations, fig.height=4}
# iterate through the length of the number of subplots 
for (i in 1:subplots){
  # initialize the mtx dataframe as an empty df 
  mtx = data.frame(matrix(ncol = 2, nrow = 0))
  # iterate through the length of the number of sheets in the current subplot 
  for (x in 1:length(sheets[[i]])){
    current_sheet = sheets[[i]][x]
    mtx1 = read_xlsx(fileNameIn1, sheet = current_sheet)
    # if the current sheet is KEGG enrichment, we want to match the ID column to the description column  
    if (grepl("KEGG", current_sheet)){
      mtx1 = mtx1 %>% 
        dplyr::mutate(ID = Description)
    }
    # filter only the terms that are present in the current list of terms 
     mtx1 = mtx1 %>% 
      dplyr::filter(ID %in% terms[[i]]) %>% 
      dplyr::mutate(log10padj = ifelse(NES < 0, 
                                       -log10(as.numeric(p.adjust)) * (-1),
                                       # create log10 padj column depending on sign of NES 
                                       -log10(as.numeric(p.adjust)))) %>%
      dplyr::select(ID, log10padj)
    # append mtx1 to mtx
     mtx = rbind(mtx, mtx1)
  }
  # Add sign variable indicating whether log10padj is negative or positive
  mtx[["sign"]] = ifelse(mtx[["log10padj"]] >= 0, "positive", "negative")
  # replace names w/shorter ones 
  mtx$ID <- gsub("GOBP_HOMOPHILIC_CELL_ADHESION_VIA_PLASMA_MEMBRANE_ADHESION_MOLECULES",
                         "GOBP_CELL_ADHESION", mtx$ID)
  # replace "GOMF_STRUCTURAL_CONSITUENT_OF_RIBOSOME" with "GOMF_RIBOSOME"
  mtx$ID <- gsub("GOMF_STRUCTURAL_CONSTITUENT_OF_RIBOSOME", "GOMF_RIBOSOME",
                         mtx$ID)
  # change Ribosome to KEGG_RIBOSOME
  mtx$ID <- gsub("Ribosome", "KEGG_RIBOSOME",
                         mtx$ID)
  # KEGG_BASAL_CELL_CARCINOMA, 
  mtx$ID <- gsub("Basal cell carcinoma", "KEGG_BASAL_CELL_CARCINOMA",
                         mtx$ID)
  
  # KEGG_RIBOSOME
  mtx$ID <- gsub("KEGG_RIBOSOME biogenesis in eukaryotes", "KEGG_RIBOSOME",
                         mtx$ID)
  # KEGG_METABOLISM_BY_XENOBIOTICS, 
  mtx$ID <- gsub("Metabolism of xenobiotics by cytochrome P450", "KEGG_METABOLISM_BY_XENOBIOTICS",
                         mtx$ID)
  #KEGG_TYROSINE_METABOLISM
  mtx$ID <- gsub("Tyrosine metabolism", "KEGG_TYROSINE_METABOLISM",
                         mtx$ID)
  # Change Oxidative phosphorylation to KEGG_OXPHOS
  mtx$ID <- gsub("Oxidative phosphorylation", "KEGG_OXPHOS", mtx$ID)
  # Adjust what name to plot
  mtx$enrichment <- str_trunc(mtx$ID, width = max_enrichment_length)
  # plot
  panel_plot = ggplot(data = mtx, aes(x = reorder(enrichment, log10padj), y = log10padj)) +
    # geom_col(aes(fill = log10padj)) +
    geom_col(aes(fill = sign), width = 0.7) +
    # scale_fill_gradient2(low = "blue", high = "red", midpoint = 0) +
    scale_fill_manual(name = "Direction",
                      values = c("positive" = mycols[2], "negative" = mycols[1]), 
                      labels = c("Duplicated", "Deleted")) +
    coord_flip() +
    theme_cowplot() +
    ylab("-log10 adjusted p-value") +
    xlab("Enrichment term") +
    theme(text = element_text(size = 25),
          axis.text = element_text(size = 20),
          legend.position = c(0.05, 0.85),
          legend.background = element_rect(fill="white", 
                                    size=0.5, linetype="solid"))
  # save plot
  fileNameOut = file.path(OutputDir, paste0(names(sheets[i]), Output_Suffix))
  ggsave(filename = fileNameOut, plot = panel_plot, width = 10, height = 4)
}

```



