---
title: "Anchor Masking"
author: "Maggie Marshall"
date: "`r Sys.Date()`"
always_allow_html: true
output:
  html_document:
    theme: cerulean
    toc: yes
  pdf_document:
    toc: no
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
# Set up the environment
library(knitr)
opts_chunk$set(cache.path = "cache/", fig.path = "img/", cache = F, tidy = T, fig.keep = "high", echo = F, dpi = 100, warnings = F, message = F, comment = NA, warning = F, results = "as.is", fig.width = 10, fig.height = 6, cache.lazy = FALSE) # out.width=700,
library(pander)
panderOptions("table.split.table", Inf)
set.seed(1)
library(dplyr)
options(stringsAsFactors = FALSE)
```

- Input: PR/CR/Common Anchors from `~/Google Drive/My Drive/HiC_files/results/datatype/preprocessing_any` where data type can be Mustache, HiCcompare, Neoloops, and SpectralTAD anchors 
- Output: `~/Google Drive/My Drive/HiC_files/results/Maggie/datatype/Motif_Enrichment/Masked_Anchors`
where data type can be Mustache, HiCcompare, Neoloops, and SpectralTAD
Bed files containing anchors "masked" with open chromatin regions using activeranges (`https://github.com/mdozmorov/activeranges`). Will be used to perform Motif enrichment using MEME & HOMER ChIP-seq. 

# Libraries

```{r libraries}
library(activeranges)
library(excluderanges)
library(GenomicRanges)
library(knitr)
library(rtracklayer)
```

# Settings

```{r}
# Maggie's paths 
# Maggie's home directory
home_dir = '~/Google Drive/My Drive'
# home_dir <- "/Users/mdozmorov/Documents/Data/GoogleDrive"

# data type parameter 
mustache <- FALSE 
mustache_v2 <- FALSE 
hiccompare <- FALSE
hiccompare_v1 <- FALSE
hiccompare_v2 <- FALSE
spectralTAD <- FALSE
spectralTAD_v2 <- FALSE
neoloop <- FALSE
neoloop_v2 <- TRUE
hicFindTADs <- FALSE
hicFindTADs_v2 <- FALSE

# preprocessing type
preprocessing = 'any'

# resolution string  
# Make it 50kb, 100kb, 200kb , 500kb for SpectralTAD window sizes 
resolution_string <- "10kb"


if (mustache) {
    dir_data <- file.path(home_dir, "HiC_files/results/mustache_results", paste0('preprocessing_',preprocessing))
    dir_results <-  file.path(home_dir, "HiC_files/results/Maggie/Mustache_results", paste0('preprocessing_',preprocessing), 'Motif_Enrichment/Masked_Anchors')
    analysis_type <- "Mustache"
  
} else if (mustache_v2) {
    dir_data <- file.path(home_dir, "HiC_files/results/mustache_results_v2", paste0('preprocessing_',preprocessing))
    dir_results <-  file.path(home_dir, "HiC_files/results/Maggie/Mustache_results_v2", paste0('preprocessing_',preprocessing), 'Motif_Enrichment/Masked_Anchors')
    analysis_type <- "Mustache_v2"
} else if (hiccompare) {
  dir_data <- file.path(home_dir, "HiC_files/results/HiCcompare_results", paste0('preprocessing_',preprocessing))
    dir_results <-  file.path(home_dir, "HiC_files/results/Maggie/HiCcompare_results", paste0('preprocessing_',preprocessing), 'Motif_Enrichment/Masked_Anchors')
    analysis_type <- "HiCcompare"
} else if (hiccompare_v1) {
  dir_data <- file.path(home_dir, "HiC_files/results/HiCcompare_results_v1", paste0('preprocessing_',preprocessing))
    dir_results <-  file.path(home_dir, "HiC_files/results/Maggie/HiCcompare_results_v1", paste0('preprocessing_',preprocessing), 'Motif_Enrichment/Masked_Anchors')
    analysis_type <- "HiCcompare_v1"
} else if (hiccompare_v2) {
  dir_data <- file.path(home_dir, "HiC_files/results/HiCcompare_results_v2", paste0('preprocessing_',preprocessing))
    dir_results <-  file.path(home_dir, "HiC_files/results/Maggie/HiCcompare_results_v2", paste0('preprocessing_',preprocessing), 'Motif_Enrichment/Masked_Anchors')
    analysis_type <- "HiCcompare_v2"
} else if (spectralTAD) {
  dir_data <- file.path(home_dir, "HiC_files/results/TAD_Boundaries/SpectralTAD", paste0('preprocessing_',preprocessing))
    dir_results <-  file.path(home_dir, "HiC_files/results/Maggie/TAD_Boundaries_Analysis/SpectralTAD_results", paste0('preprocessing_',preprocessing), 'Motif_Enrichment/Masked_Anchors')
    analysis_type <- "SpectralTAD"
} else if (spectralTAD_v2) {
  dir_data <- file.path(home_dir, "HiC_files/results/TAD_Boundaries/SpectralTAD_v2", paste0('preprocessing_',preprocessing))
    dir_results <-  file.path(home_dir, "HiC_files/results/Maggie/TAD_Boundaries_Analysis/SpectralTAD_results_v2", paste0('preprocessing_',preprocessing), 'Motif_Enrichment/Masked_Anchors')
    analysis_type <- "SpectralTAD_v2"
} else if (neoloop) {
  resolution_string <- "10kb" # can keep for now, only have 10kb anchors
  dir_data <- file.path(home_dir, "HiC_files/results/neoloopfinder_results", paste0('preprocessing_',preprocessing))
    dir_results <-  file.path(home_dir, "HiC_files/results/Maggie/Neoloop_results", paste0('preprocessing_',preprocessing), 'Motif_Enrichment/Masked_Anchors')
    analysis_type <- "Neoloop"
} else if (neoloop_v2) {
  resolution_string <- "10kb" # can keep for now, only have 10kb anchors
  dir_data <- file.path(home_dir, "HiC_files/results/neoloopfinder_results_v2", paste0('preprocessing_',preprocessing))
    dir_results <-  file.path(home_dir, "HiC_files/results/Maggie/Neoloop_results_v2", paste0('preprocessing_',preprocessing), 'Motif_Enrichment/Masked_Anchors')
    analysis_type <- "Neoloop_v2"
} else if (hicFindTADs){
  dir_data <- file.path(home_dir, "HiC_files/results/TAD_Boundaries/hicFindTADs", paste0('preprocessing_',preprocessing))
    dir_results <-  file.path(home_dir, "HiC_files/results/Maggie/TAD_Boundaries_Analysis/hicFindTADs_results", paste0('preprocessing_',preprocessing), 'Motif_Enrichment/Masked_Anchors')
    analysis_type <- "hicFindTADs"
}else if (hicFindTADs_v2){
  dir_data <- file.path(home_dir, "HiC_files/results/TAD_Boundaries/hicFindTADs_v2", paste0('preprocessing_',preprocessing))
    dir_results <-  file.path(home_dir, "HiC_files/results/Maggie/TAD_Boundaries_Analysis/hicFindTADs_results_v2", paste0('preprocessing_',preprocessing), 'Motif_Enrichment/Masked_Anchors')
    analysis_type <- "hicFindTADs_v2"
}

# set input files 
PR_file <- file.path(dir_data, paste0("anchors_PR_unique_", resolution_string, ".bed"))
CR_file <- file.path(dir_data, paste0("anchors_CR_unique_", resolution_string, ".bed"))
PR_Common_file <- file.path(dir_data, paste0("anchors_PR_common_", resolution_string, ".bed"))
CR_Common_file <- file.path(dir_data, paste0("anchors_CR_common_", resolution_string, ".bed"))
# set output files 
PR_output <- file.path(dir_results, paste0("masked_PR_anchors_", resolution_string,".bed"))
CR_output <- file.path(dir_results, paste0("masked_CR_anchors_", resolution_string,".bed"))
PR_Common_output <- file.path(dir_results, paste0("masked_PR_Common_anchors_", resolution_string,".bed"))
CR_Common_output <- file.path(dir_results, paste0("masked_CR_Common_anchors_", resolution_string,".bed"))
```

# Load in hg38 activeranges coordinates
```{r}
# hg38 activeranges coordinates
download.file(url = "https://drive.google.com/uc?export=download&id=1CdaSUr45IbmDicegz0TPITcOO41e2MaT", destfile = "misc/hg38.Meuleman.Cancer_epithelial.rds")
ActiveGR.hg38.Cancer <- readRDS(file = "misc/hg38.Meuleman.Cancer_epithelial.rds")
ActiveGR.hg38.Cancer
```

# Load in hg38 excluderanges

```{r}
# hg38 centromere 
suppressPackageStartupMessages(library(rCGH))
suppressPackageStartupMessages(library(GenomicRanges))
# hg38 # data.frame
# Adjust chromosome names
hg38$chrom[hg38$chrom == 23] <- "X"
hg38$chrom[hg38$chrom == 24] <- "Y"
hg38$chrom <- paste0("chr", hg38$chrom)
# Make GRanges object
hg38.UCSC.centromere <- makeGRangesFromDataFrame(hg38, seqnames.field = "chrom", start.field = "centromerStart", end.field = "centromerEnd")
# Assign seqinfo data
seqlengths(hg38.UCSC.centromere) <- hg38$length
genome(hg38.UCSC.centromere)     <- "hg38"
# Resulting object
hg38.UCSC.centromere

# hg38 telomere 
download.file(url = "https://drive.google.com/uc?id=1Hn8D81TlBbbdbSVfIJTxWxUpFKxzyM0L&export=download", destfile = "misc/hg38.UCSC.telomere.rds")
hg38.UCSC.telomere <- readRDS(file = "misc/hg38.UCSC.telomere.rds")
hg38.UCSC.telomere
```

# Files 

Read in anchor files into tables 

```{r files}
PR = read.table(PR_file, header = FALSE, sep="\t",stringsAsFactors=FALSE, quote="", skip = 1)
CR = read.table(CR_file, header = FALSE, sep="\t",stringsAsFactors=FALSE, quote="", skip = 1)
PR_Common = read.table(PR_Common_file, header = FALSE, sep="\t",stringsAsFactors=FALSE, quote="", skip = 1)
CR_Common = read.table(CR_Common_file, header = FALSE, sep="\t",stringsAsFactors=FALSE, quote="", skip = 1)
```

# Build GRanges

```{r granges}
GR_PR <- GRanges(seqnames=PR$V1, 
                      ranges= IRanges(start=PR$V2, end=PR$V3)) 
GR_CR <- GRanges(seqnames=CR$V1, 
                      ranges= IRanges(start=CR$V2, end=CR$V3))
GR_PR_Common <- GRanges(seqnames=PR_Common$V1, 
                      ranges= IRanges(start=PR_Common$V2, end=PR_Common$V3)) 
GR_CR_Common <- GRanges(seqnames=CR_Common$V1, 
                      ranges= IRanges(start=CR_Common$V2, end=CR_Common$V3)) 
```

# Number of anchors that intersect with ATAC-seq & Exclude Regions

Use subsetByOverlaps because it will select only certain ranges from the GRanges that overlap with the ATAC-seq & Exclude regions 

```{r activeexclude}
# Make empty dataframe to show the number of total anchors, the anchors overlapping ATAC-seq, overlapping Centromeres, and overlapping telomeres 
#create data frame with 0 rows and 4 columns
df <- data.frame(matrix(ncol = 4, nrow = 0))

print(resolution_string)
print(analysis_type)

print("Number of PR Anchors")
PR_length <- length(GR_PR)
print("Number of PR anchors overlapping ATC-seq Regions")
PR_atac <- length(subsetByOverlaps(GR_PR, ActiveGR.hg38.Cancer))
print("Number of PR anchors overlapping Centromeres")
PR_centro <- length(subsetByOverlaps(GR_PR, hg38.UCSC.centromere))
print("Number of PR anchors overlapping Telomeres")
PR_telo <- length(subsetByOverlaps(GR_PR, hg38.UCSC.telomere))
 df <- rbind(df, c(PR_length, PR_atac, PR_centro, PR_telo))

print("Number of CR Anchors")
CR_length <- length(GR_CR)
print("Number of CR anchors overlapping ATC-seq Regions")
CR_atac <- length(subsetByOverlaps(GR_CR, ActiveGR.hg38.Cancer))
print("Number of CR anchors overlapping Centromeres")
CR_centro <- length(subsetByOverlaps(GR_CR, hg38.UCSC.centromere))
print("Number of CR anchors overlapping Telomeres")
CR_telo <- length(subsetByOverlaps(GR_CR, hg38.UCSC.telomere))
df <- rbind(df, c(CR_length, CR_atac, CR_centro, CR_telo))

print("Number of PR Common Anchors")
PR_Common_length <- length(GR_PR_Common)
print("Number of PR Common anchors overlapping ATC-seq Regions")
PR_Common_atac <- length(subsetByOverlaps(GR_PR_Common, ActiveGR.hg38.Cancer))
print("Number of PR Common anchors overlapping Centromeres")
PR_Common_centro <- length(subsetByOverlaps(GR_PR_Common, hg38.UCSC.centromere))
print("Number of PR Common anchors overlapping Telomeres")
PR_Common_telo <- length(subsetByOverlaps(GR_PR_Common, hg38.UCSC.telomere))
df <- rbind(df, c(PR_Common_length, PR_Common_atac, PR_Common_centro, PR_Common_telo)) 


print("Number of CR Common Anchors")
CR_Common_length <- length(GR_CR_Common)
print("Number of CR Common anchors overlapping ATC-seq Regions")
CR_Common_atac <- length(subsetByOverlaps(GR_CR_Common, ActiveGR.hg38.Cancer))
print("Number of CR Common anchors overlapping Centromeres")
CR_Common_centro <- length(subsetByOverlaps(GR_CR_Common, hg38.UCSC.centromere))
print("Number of CR Common anchors overlapping Telomeres")
CR_Common_telo <- length(subsetByOverlaps(GR_CR_Common, hg38.UCSC.telomere))
df <- rbind(df, c(CR_Common_length, CR_Common_atac, CR_Common_centro, CR_Common_telo)) 
colnames(df) <- c('Total', 'Overlapping_ATAC_Seq', 'Overlapping_Centromeres', 'Overlapping_Telomeres')



knitr::kable(df)
```

# Reduce Anchors

```{r reduce}
GR_PR <- GR_PR %>% GenomicRanges::reduce()
GR_CR <- GR_CR %>% GenomicRanges::reduce()
GR_PR_Common <- GR_PR_Common %>% GenomicRanges::reduce()
GR_CR_Common <- GR_CR_Common %>% GenomicRanges::reduce()
```

# Intersect with hg38.Meuleman.Cancer_epithelial.rds

This will allow for only the open-chromatin regions to be saved from the anchors. 

```{r intersect}
masked_PR <- intersect(GR_PR, ActiveGR.hg38.Cancer)
masked_CR <- intersect(GR_CR, ActiveGR.hg38.Cancer)
masked_PR_Common <- intersect(GR_PR_Common, ActiveGR.hg38.Cancer)
masked_CR_Common <- intersect(GR_CR_Common, ActiveGR.hg38.Cancer)
```

# Save Masked Bed Files

```{r export}
export.bed(masked_PR, PR_output)
export.bed(masked_CR, CR_output)
export.bed(masked_PR_Common, PR_Common_output)
export.bed(masked_CR_Common, CR_Common_output)
```
