---
title: "Combined Gene Enrichment Barplots"
author: "Maggie Marshall"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: no
  html_document:
    theme: cerulean
    toc: yes
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
# Set up the environment
library(knitr)
opts_chunk$set(cache.path='cache/', fig.path='img/', cache=F, tidy=T, fig.keep='high', echo=F, dpi=100, warnings=F, message=F, comment=NA, warning=F, results='as.is', fig.width = 10, fig.height = 6) #out.width=700, 
library(pander)
panderOptions('table.split.table', Inf)
set.seed(1)
library(tidyverse)
options(stringsAsFactors = FALSE)
```

Visualized gene enrichments done on important genes found in different analyses (RNA seq, WGS, etc.) for PR and CR conditions in Supplementary Table 6. 

For PR: 
KEGG: Influenza A
C2: NIKOLSKY_BREAST_CANCER_22Q13_AMPLICON
HALLMARK: Interferon GAMMA_RESPONSE

For CR: 
KEGG: Ribosome
KEGG: Oxidative phosphorylation
C2: Nikolsky BREAST_CANCER 17q21-q25 AMPLICON

Each condition will be its own separate plot. 

# Libraries 

```{r lib}
library(ggplot2)
library(readxl)
library("ggsci")
library(scales)
scales::show_col(pal_lancet("lanonc")(8))
mycols = pal_lancet("lanonc")(8)
library(forcats)
library(purrr)
library(cowplot)
```


# Settings 

```{r settings}
# Data directory 
# Maggie's 
data_dir = "~/Google Drive/My Drive/HiC_files/results/manuscript/Supplementary_Table_6"
# output directory to save plots, Figure 7 folder 
output_dir = "~/Google Drive/My Drive/HiC_files/results/manuscript/Figure_7"
# condition parameter 
condition = "PR"
# condition = "CR"
# set bar plot fill parameter depending on condition, PR = blue, CR = red 
bar_fill = ifelse(condition == "PR", mycols[1], mycols[2])
# set sheet names to read in depending on condition and pathways to select for 
if (condition == "PR"){
  sheet_names = c("PR.KEGG", "PR.C2", "PR.H")
  pathways = c("Influenza A", "HALLMARK_INTERFERON_GAMMA_RESPONSE", "NIKOLSKY_BREAST_CANCER_22Q13_AMPLICON")
  pathway_plot_names = c("KEGG: Influenza A", "HALLMARK: Interferon \ngamma response", 
                         "C2: Nikolsky breast cancer \n 22q13 amplicon")
} else{
  sheet_names = c("CR.KEGG", "CR.C2")
  pathways = c("NIKOLSKY_BREAST_CANCER_17Q21_Q25_AMPLICON", "Ribosome", "Oxidative phosphorylation")
  pathway_plot_names = c("C2: Nikolsky breast cancer \n 17q21-q25 amplicon", "KEGG: Ribosome", 
                         "KEGG: Oxidative \nphosphorylation")
}
# enrichment file, supp table 6
enrichmentFile = file.path(data_dir, "Supplementary_Table_6.xlsx")
# output plot 
outputPlot = file.path(output_dir, paste0(condition, "_tableS6_enrichment_barplot.svg"))
```

# Read in the file 

```{r file}
# iterate through each sheet in sheet_names and read it in as a dataframe then add the dataframe to the mtx dataframe
mtx = data.frame(matrix(ncol = 2, nrow = 0))
for (i in 1:length(sheet_names)){
  # read in the current sheet into a dataframe 
  mtx1 = read_xlsx(enrichmentFile, sheet = sheet_names[i])
  # change the Term name to ID if it's KEGG 
  colnames(mtx1)[1] = "ID"
  # filter to contain only IDs that are in the pathways vector 
  mtx1 = mtx1 %>% 
    dplyr::filter(ID %in% pathways) 
  # if current sheet is KEGG get the Adjusted.P.value column and rename to p.adjust
  if (grepl("KEGG",sheet_names[i])) {
    mtx1 = mtx1 %>% 
      dplyr::mutate(p.adjust = Adjusted.P.value)
  }
  # select only the ID and p.adjust columns, only ones we need 
  mtx1 = mtx1 %>% 
    dplyr::select(ID, p.adjust)
  # combine mtx1 with mtx
  mtx = rbind(mtx, mtx1) %>% 
    arrange(ID)
}
# add -log10(padjusted) column to matrix 
mtx = mtx %>% 
  dplyr::mutate(log10pvalue = -log10(p.adjust)) %>% 
  dplyr::arrange(desc(log10pvalue))
```


# Visualization 

```{r vis}
panel_plot = ggplot(data = mtx, aes(x = reorder(ID, log10pvalue), y = log10pvalue)) +
    geom_col(fill = bar_fill, width = 0.5) +
    coord_flip() +
    theme_cowplot() +
    ylab("-log10 adjusted p-value") +
    xlab("Enrichment term") +
    theme(text = element_text(size = 20),
          axis.text = element_text(size = 15),
          legend.position = c(0.05, 0.85),
          legend.background = element_rect(fill="white", 
                                    size=0.5, linetype="solid")) +
  scale_x_discrete(breaks = pathways, 
                   labels = pathway_plot_names)
ggsave(plot = panel_plot, filename = outputPlot, width = 8, height = 3)
```


