---
title: "Anchor & Loop Bar Plots"
author: "Maggie Marshall"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cerulean
    toc: yes
  pdf_document:
    toc: no
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
# Set up the environment
library(knitr)
opts_chunk$set(cache.path = "cache/", fig.path = "img/", cache = F, tidy = T, fig.keep = "high", echo = F, dpi = 100, warnings = F, message = F, comment = NA, warning = F, results = "as.is", fig.width = 5, fig.height = 3, cache.lazy = FALSE) # out.width=700,
library(pander)
panderOptions("table.split.table", Inf)
set.seed(1)
library(dplyr)
options(stringsAsFactors = FALSE)
options(scipen=10000)
```

This script creates stacked bar plots showing the counts of CR (CR unique & CR common) and PR (PR unique and PR common) anchor and loops for each data type/resolution. Takes in the file `log_*` that contains the counts of anchors and loops for each condition and resolution (res) for the specified data type (XX)

# Libraries 

```{r lib}
library(tidyverse)
library(ggplot2)
library("ggsci")
library(scales)
scales::show_col(pal_lancet("lanonc")(8))
mycols = pal_lancet("lanonc")(8)
library(forcats)
```

# Settings

```{r settings}
# Maggie's home directory
home_dir = '~/Google Drive/My Drive'
# Mikhail's home directory
# home_dir <- "/Users/mdozmorov/Documents/Data/GoogleDrive"
# data type parameter, comment out for whichever one is being used 
data_type = "Mustache_v2"
# data_type = "HiCcompare_v2"
# preprocessing parameter, so far any is the only one 
preprocessing = "any"
# resolution parameter
resolution = "10kb"

# set data directory depending on data type, results will be saved in same directory
if (data_type == "Mustache_v2"){
  data_dir = file.path(home_dir, 'HiC_files/results/mustache_results_v2', paste0('preprocessing_', preprocessing))
} else if (data_type == "HiCcompare_v2"){
  data_dir = file.path(home_dir, 'HiC_files/results/HiCcompare_results_v2', paste0('preprocessing_', preprocessing))
}
```

# Read in the log file containing anchor and loop counts & reformat data frame

```{r file}
# read in the file, since there is an unequal # of columns we have to do fill = TRUE and manually name the columns 
logFile = read.table(file.path(data_dir, paste0("log_", resolution, ".csv")), 
                     header = FALSE, sep = ",", fill = TRUE, col.names = paste0("V",seq_len(5))) %>% 
  # select only the two columns we need
  dplyr::select(V1, V2) %>% 
  # pivot wider to get the values from V1 to the column names and the values from V2 to be each column's value for easy accessibility 
  pivot_wider(names_from = V1,
              values_from = V2)

# create a new dataframe for loop and anchors where there are three columns, one for the condition (PR or CR), one for whether it is unique or common, and one for the value 
# create first column 
conditions = c("PR", "PR", "CR", "CR")
# create column indicating unique or common
shared = c("Unique", "Common", "Unique", "Common")
# create column for that value for loops
loops_value = c(logFile$`Loops PR unique count`, logFile$`Loops PR common count`, logFile$`Loops CR unique count`, logFile$`Loops CR common count`)
# create column for that value for anchors 
anchors_value = c(logFile$`Anchors PR unique count`, logFile$`Anchors PR common count`, logFile$`Anchors CR unique count`, logFile$`Anchors CR common count`)
# make dataframe for loops 
loops_df = data.frame(conditions, shared, loops_value) 
# make dataframe for anchors 
anchors_df = data.frame(conditions, shared, anchors_value)
```

# Create the bar plots for anchors & loops 

```{r barplots}
# create loops bar plot 
loopBP = loops_df %>% 
  ggplot(aes(fill = forcats::fct_rev(shared), y = loops_value, x = conditions)) +
  geom_bar(position = "stack", stat="identity", width = 0.35) + 
  theme_bw() +
  # get rid of the grid 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        text = element_text(size = 13),
        plot.title=element_text(hjust=0.5)) +
  ylab("Count") +
  xlab("") +
  ggtitle("Loops") +
  scale_fill_manual(values = rev(mycols[1:2]), name = "") + # get rid of legend title
  scale_x_discrete(limits = c("PR", "CR"), 
                   labels=c("Primary Tumor", "Carboplatin Resistant")) # reorder the x axis & change labels 
# save the loop barplot
ggsave(filename = file.path(data_dir, paste0("log_", resolution, "_loops_barplot.svg")), plot = loopBP, width = 5, height = 3)

# create anchors bar plot 
anchorBP = anchors_df %>% 
  ggplot(aes(fill = forcats::fct_rev(shared), y = anchors_value, x = conditions)) +
  geom_bar(position = "stack", stat="identity", width = 0.35) + 
  theme_bw() +
  # get rid of the grid 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
         text = element_text(size = 13),
        plot.title=element_text(hjust=0.5)) +
  ylab("Count") +
  xlab("") +
  ggtitle("Anchors") +
  scale_fill_manual(values = rev(mycols[1:2]), name = "") + # get rid of legend title 
  scale_x_discrete(limits = c("PR", "CR"),
                   labels=c("Primary Tumor", "Carboplatin Resistant")) # reorder the x axis & change labels
# save the anchors barplot
ggsave(filename = file.path(data_dir, paste0("log_", resolution, "_anchors_barplot.svg")), plot = anchorBP, width = 5, height = 3)
```

